---
title: "LEPAS Zooplankton Data Entry 2020"
output: html_document
---

#### LEPAS data entry ####
This code enters zooplankton data into the LEPAS database. These front-end functions and the back-end script 
"Zooplankton_data_entry_functions_2020.R" were modified from Dr. Josh Stone's original versions in January, 2020 
by Dr. Daniel. R. O'Donnell to be compatible with the overhauled "LEPAS_2020" SQLite database (LEPAS_2020.db), and 
to accomodate batch submission of datasheets.

Please follow the steps outlined below:

1. Enter the the sampling year (e.g. "2020") and the correct Lake Erie basin (e.g. "WB"). 

2. Make sure the file paths below (in the 'FilePath', "FileName', 'Database', and 'source' lines) point to the correct 
   data entry spreadsheets and folders that you wish to enter into the database. 

**Only use the correctly formatted data entry sheet that has been provided.**

3. Run the code below by pressing the green arrow -> at the right side of the grey code box.   
```{r warning=FALSE}

Year <- "2019"
Basin <- "CB"
# FileNames <- c("20190422-1279_20m.xlsx","20190422-1281_10m.xlsx","20190506-1279_20m.xlsx","20190524-1279_20m.xlsx","20190606-1279_20m.xlsx")
# FileNames <- c("20190422-1279_20m.csv","20190422-1281_10m.csv","20190506-1279_20m.csv","20190524-1279_20m.csv","20190606-1279_20m.csv")
FileNames <- c("20190422-1279_20m.csv")
FilePath <- paste0("Z:\\Projects\\FADX09_LEPAS\\15-LEPAS Datasheets\\Entered Spreadsheets\\3-Zooplankton\\LEPAS_2019\\2019-CB\\NOT_entered\\")
Database <- paste0("Z:\\Projects\\FADX09_LEPAS\\2-Finalized_data\\LEPAS_2020 - Copy.db")
source("Z:\\Projects\\FADX09_LEPAS\\7-Data Entry\\Zooplankton_2020\\Zooplankton_data_entry_functions_2020.R")

step1(FileNames)

```


#### Data Check 1 ####
4. Check that the data have been entered properly, and that 'Number Measured OK' is displayed above for each datasheet.
   
5. Type "OK" (including quotes) into the parentheses after 'input1' in the line below and run 
   the code by pressing the green arrow.

```{r}

input1("OK")

```


6. If data have been successfully entered, run the step2 code below by pressing the green arrow.

```{r}

step2(X)

```


#### Data Check 2 ####
7. Check that the data have been entered properly. Look at table titled 'Zoop_final'.
8. Type "OK" into the parentheses after 'input2' in the line below and run the code by pressing the green arrow.

**This code will also write the datasheet to a .csv and send it to the "Entered" folder**

```{r}

input2("OK")

```





